---
title: "Readme"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
Getting and Cleaning Data - Course Project
This repository hosts the R code and documentation files for the Data Science's track course "Getting and Cleaning data", available in coursera.
The dataset being used is: Human Activity Recognition Using Smartphones
Files
This has  all the data for this project in the same folder, un-compressed and without names altered.
CodeBook.md describes the variables, the data, and any transformations or work that was performed to clean up the data.
run_analysis.R contains all the code to perform the analyses described in the 5 steps. 
The output of the 5th step is called tidydata.txt, and uploaded in the course project's form.


## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
